Understanding Factors Contributing to DineSafe Violation Severity

### 2024-11-22 paper/paper.qmd
updated appendix

- Institutional food preparation: college/uni food services, child care, institutional food service, cafeteria priv, cafeteria public, student nutrition site, secondary school food services, child care food prep, hospitals and health facilities, elementary school food services, hospital and health facilities, church banquet facility,  Other Educational Facility Food Services, rest home, nursing home, serving kitchen, community kitchen, food caterer, boarding/lodging, food bank, serving kitchen, private club, centralized kitchen, retirement homes, commissary

>>>>

- Institutional food preparation: college/university food services, child care, institutional food service, cafeteria private, cafeteria public, student nutrition site, secondary school food services, child care food preparation, hospitals and health facilities, elementary school food services, hospital and health facilities, church banquet facility,  other educational facility food services, rest home, nursing home, serving kitchen, community kitchen, food caterer, boarding/lodging, food bank, serving kitchen, private club, centralized kitchen, retirement homes, commissary
